Viscous Transport in Eroding Porous Media

### 2019-05-17 docs/transport/erosion_transport.tex
worked on numerics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to include historically significant reference Shelley \cite{baker1986boundary}).
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing with our previous work~\cite{qua-moo2018}, we use a
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
normal at $\yy$, and $\eeta$ is an unknown density function.  In
Section~\ref{sec:DLPcomplex}, we show how the Stokes double-layer
potential can also be expressed as the sum of a Laplacian double-layer
potential 
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy
\end{align}
and its gradient.  Since the Laplacian double-layer potential can be
written as a Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,
  \label{eqn:laplaceComplex}
\end{align}
where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
the Stokes double-layer potential can be written in terms of Cauchy
integrals and its first derivative.  We also require the derivative of
the Stokes double-layer potential which requires the second derivative
of Cauchy integrals.

We will be using quadrature formulae to compute $v$ and its derivatives
that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
value only depends on its boundary data.  The boundary data satisfies
the Sokhotski-Plemelj jump relation
\begin{align}
  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Once the boundary data of $v$ is computed, we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
function defined in equation~\eqref{eqn:laplaceComplex}, and the
derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
\label{sec:DLPcomplex}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\bd\Omega} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\bd\Omega}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
\end{align}
All these integrals but the first are a gradient of a Laplace layer
potential.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued density
function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  \label{eqn:cauchy1}
  u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
  u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have shown that the velocity, shear stress, vorticity, and pressure
of the double-layer potential can all be written in terms of Cauchy
integrals and its first two derivatives.  Therefore, we require
quadrature methods to evaluate the expressions in
equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
periodic, the Trapezoid rule has spectral accuracy.  However, the
integrand is nearly singular if $x$ is close to $\bd\Omega$, and the
quadrature error is arbitrarily large if the resolution $N$ is fixed.
There have been a variety of near-singular integration schemes
developed, and we extend a method first outlined by Barnett et
al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
rule}.  This method first uses the density function $\tau(y)$ to compute
the boundary data of $v$, denoted by $v^-{y}$.  Then, it makes use
of the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega.
\end{align}

Here, we briefly describe this quadrature method, and then derive a
necessary extension to simulate erosion.  The Barycentric quadrature
rule starts with a quadrature rule with nodes $y_j \in \bd\Omega$ and
weights $w_j$. We use the trapezoid rule because of its superior
accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, as $x$
approaches $\bd\Omega$, the integrand becomes nearly singular and the
quality of the trapezoid rule deteriorates. To eliminate the
nearly-singular integrand, we use the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
\end{align}
Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
nearly-singular and the accuracy of the trapezoid rule is bounded
independent of $x$.  A similar identity identity involving $v'(x)$ also
holds.   Now, applying the spectrally accurate trapezoid rule, the
quadrature error of the Barycentric quadrature rule
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}
  \quad \text{and} \quad
  v'(x) \approx \frac{\sum\limits_{j=1}^N 
    \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
  \label{eqn:vvpQuadrature}
\end{align}
is uniformly bounded~\cite{bar-wu-vee2015}.  A slight modification of
these formulae are applied if $x \in \Omega^{c}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
developed~\cite{bar-wu-vee2015}, this work requires a similar quadrature
rule for $v''(x)$.  We mimic the approach developed
in~\cite{bar-wu-vee2015}.  First, if $x \in \Omega$ and $n \in
\mathbb{N}$, then 
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n > 1. \\
    \end{array}
  \right.
\end{align}
Applying this identity to the Cauchy integral theorem for $v''(x)$, we
have
\begin{align}
  0 &= \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
%    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2v(x)}{(y-x)^3}\, dy -
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
Since we have constructed the integrand so that it is bounded for for
all $x \in \Omega$, the quadrature error of the trapezoid rule is
acceptable.  Applying the quadrature rule and solving for $v''(x)$, the
Barycentric quadrature rule for the second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
\end{align}
To compute $v(x)$ and $v'(x)$, the Barycentric quadrature rule in
equation~\eqref{eqn:vvpQuadrature} is used. If $x \in \Omega^c$, the
identity
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x} dy, 
\end{align}
is used, and the resulting Barycentric quadrature formula is
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
\end{align}

@@

To compute the velocity with $\mathcal{O}(N)$ operations, we start by
using the trapezoid rule accelerated with the fast multipole method
(FMM) \todo[inline]{reference here}. For target points that are
sufficiently far from $\bd\Omega$, the resulting velocity is
sufficiently accurate.  However, the velocity at points that are too
close to $\bd\Omega$ must be corrected.  For a general point $\xx$,
\begin{align}
  \vv(\xx) = \int_{\Gamma} D(\xx,\yy) \eeta(\yy)\, ds_\yy + 
    \sum_{k=1}^{M} \int_{\gamma_k} D(\xx,\yy) \eeta(\yy)\, ds_\yy.
\end{align}
Assuming that $\xx$ is too close to $\gamma_i$, we first subtract the
velocity contribution of $\vv(\xx)$ due to $\gamma_i$.  Then, the
Barycentric quadrature rule is used to compute the velocity due to
$\gamma_i$ with more accuracy.  This is correction is applied to all
points that are close to an eroding body or the outer wall $\Gamma$.

The same strategy of using the trapezoid rule and then correcting with
the Barycentric quadrature is used to compute the shear stress on
$\bd\Omega$ and vorticity in $\Omega$.  The trapezoid rule is applied
with a direct summation, but this cost is only incurred once per time
step, and the majority of the computational effort is still required to
compute the velocity using the fast summation method.

@@

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}
{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to
    include historically significant reference Shelley
    \cite{baker1986boundary}).  Also need discuss Helsing and Ojala who
    did a similar panel-based quadrature~\cite{hel-oja2008}
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing with our previous work~\cite{qua-moo2018}, we use a
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) = 
    \int_{\bd\Omega} D(\xx,\yy) \eeta(\yy)\, ds_\yy = 
  \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $D$ is the kernel of the integral operator, $\rr = \xx - \yy$,
$\rho = \|\rr\|$, $\nn$ is the unit outward normal at $\yy$, and $\eeta$
is an unknown density function.  In Section~\ref{sec:DLPcomplex}, we
show how the Stokes double-layer potential can also be expressed as the
sum of a Laplacian double-layer potential 
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy
\end{align}
and its gradient.  Since the Laplacian double-layer potential can be
written as a Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,
  \label{eqn:laplaceComplex}
\end{align}
where $\xx,\yy \in \RR^2$ are identified with the points $x,y \in \CC$,
the Stokes double-layer potential can be written in terms of Cauchy
integrals and its first derivative.  We also require the derivative of
the Stokes double-layer potential which requires the second derivative
of Cauchy integrals.

We will be using quadrature formulae to compute $v$ and its derivatives
that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
value only depends on its boundary data.  The boundary data satisfies
the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Once the boundary data of $v$ is computed, we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
function defined in equation~\eqref{eqn:laplaceComplex}, and the
derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
\label{sec:DLPcomplex}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{equation}
  \label{eqn:Stokes2Laplace}
  \begin{aligned}
    \DDD[\eeta](\xx) &= 
      \frac{1}{2\pi} \int_{\bd\Omega} 
        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
  \end{aligned}
\end{equation}
All these integrals but the first are a gradient of a Laplace layer
potential.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued density
function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  \label{eqn:cauchy1}
  u_1(x) &= \Re (v[\tau_1](x)) + \Re (v'[y\cdot\eta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
  u_2(x) &= \Re (v[\tau_2](x)) - \Im (v'[y\cdot\eta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where $y \cdot \eta = y_1 \eta_1 + i y_2 \eta_2 \in \CC$, 
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have shown that the velocity, shear stress, vorticity, and pressure
of the double-layer potential can all be written in terms of Cauchy
integrals and its first two derivatives.  Therefore, we require
quadrature methods to evaluate the expressions in
equation~\eqref{eqn:cauchy}.  Since the integrands are all smooth and
periodic, the Trapezoid rule has spectral accuracy.  However, the
integrand is nearly singular if $x$ is close to $\bd\Omega$, and the
quadrature error is arbitrarily large if the resolution $N$ is fixed.
There have been a variety of near-singular integration schemes
developed, and we extend a method first outlined by Barnett et
al.~\cite{bar-wu-vee2015} which we call the {\em Barycentric quadrature
rule}.  This method first uses the density function $\tau(y)$ to compute
the boundary data of $v$, denoted by $v^-(y)$.  Then, it makes use
of the identity
\begin{align}
  v(x) = \int_{\bd\Omega} \frac{v^{-}(y)}{y-x} \, dy, 
  \quad x \in \Omega.
\end{align}

Here, we briefly describe this quadrature method, and then derive a
necessary extension to simulate erosion.  The Barycentric quadrature
rule starts with a quadrature rule with nodes $y_j \in \bd\Omega$ and
weights $w_j$. We use the trapezoid rule because of its superior
accuracy when $x$ is sufficiently far from $\bd\Omega$.  However, as $x$
approaches $\bd\Omega$, the integrand becomes nearly singular and the
quality of the trapezoid rule deteriorates. To eliminate the
nearly-singular integrand, we use the identity
\begin{align}
  \int_{\bd\Omega} \frac{v^{-}(y) - v(x)}{y - x} \,dy = 0.
\end{align}
Rearranging for $v(x)$, we have
\begin{align}
  v(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y)}{y-x}\, dy}
    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
\end{align}
Of course, the denominator is simply $1$, but applying a quadrature rule
to both integrands results in a uniform bound on the quadrature error.
Differentiating Cauchy's integral theorem, the derivative of $v$ is
\begin{align}
  v'(x) = \frac{\int\limits_{\bd\Omega} \frac{v^{-}(y) - v(x)}{(y-x)^2}\, dy}
    {\int\limits_{\bd\Omega} \frac{1}{y-x}\, dy}.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\label{s:spatialDiscretization}
By using an integral equation formulation, we only have to discretize
the boundary of the domain.  Therefore, we only have to discretize
one-dimensional closed-curves, allowing us to use the spectrally
accurate trapezoid rule~\cite{tre-wei2014} and Fourier differentiation.
Moreover, since we only discretize the boundary of the domain, resolving
the complex eroding bodies is straightforward.

Consider eroding bodies $\gamma_k$, $k=1,\ldots,M$, in a fluid domain
$\Omega$ with boundary $\Gamma$.  Let the length of $\Gamma$ be $L_{0}$,
and the length of $\gamma_k$ be $L_k$.  We discretize each eroding body
$\gamma_k$ with $N_\iin$ points and discretize $\Gamma$ with $N_\out$
points.  The $j^{th}$ discretization point on $\Gamma$ is denoted by
$\yy_j^0$, and the $j^{th}$ discretization point on $\gamma_k$ is
denoted by $\yy^k_j$.  The discretization points are initially
distributed evenly in arclength, and this equispacing is maintained for
the entire simulation by using a {\thL}
formulation~\cite{hou-low-she1994}.  In addition, we apply mild
smoothing strategies~\cite{qua-moo2018} to avoid the corners that
erosion inevitably develop.    Since the points are equispaced, the
trapezoid rule to evaluate the velocity at a target point $\xx$ is
\begin{align}
  \label{eqn:trap}
  \uu(\xx) \approx \frac{L_0}{N_\out} \sum_{j=1}^{N_\out} 
    D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    D(\xx,\yy^k_j) \eeta^k_j,
\end{align}
where $D$ is the kernel of the Stokes double-layer potential defined in
Equation~\eqref{eqn:stokesDLP}.

As previously mentioned, the quadrature error of the trapezoid rule is
large if $\xx$ is close to $\bd\Omega$.  The proximity between $\xx$ and
$\bd\Omega$ occurs in dense packings, and also when evaluating the
velocity in the fluid bulk.  For these nearby points, instead of
applying the trapezoid rule, the Barycentric quadrature rule is applied.
In particular, the Stokes double-layer potential is decomposed into
Laplacian double-layer potentials~\eqref{eqn:Stokes2Laplace}.  Then, for
each of these Laplacian double-layer potentials, the density function is
used to find the boundary values of the analytic function whose real
part is the layer potential of interest~\eqref{eqn:SPrelation}.
Finally, instead of applying the trapezoid rule to compute the Cauchy
integrals, the quadrature rule outlined by Barnet et.~al is used
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}
  \quad \text{and} \quad
  v'(x) \approx \frac{\sum\limits_{j=1}^N 
    \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
  \label{eqn:vvpQuadrature}
\end{align}
Then, even if $x$ is close to $\bd\Omega$, the integrand is no longer
nearly-singular and the accuracy of the trapezoid rule is bounded
independent of $x$.  A similar identity identity involving $v'(x)$ also
holds.   Now, applying the spectrally accurate trapezoid rule, the
quadrature error of the Barycentric quadrature rule
is uniformly bounded~\cite{bar-wu-vee2015}.  A slight modification of
these formulae are applied if $x \in \Omega^{c}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barycentric Quadrature for $v''(x)$}
While accurate quadrature rules for $v(x)$ and $v'(x)$ have already been
developed~\cite{bar-wu-vee2015}, computing the shear stress and
vorticity requires a Barycentric quadrature rule for $v''(x)$.  We mimic
the approach developed in~\cite{bar-wu-vee2015}.  First, if $x \in
\Omega$ and $n \in \mathbb{N}$, then 
\begin{align}
  \frac{1}{2\pi i}\int_{\bd\Omega} \frac{1}{(y-x)^n}\, dy = 
  \left\{
    \begin{array}{ll}
      1, & n = 1, \\
      0, & n > 1. \\
    \end{array}
  \right.
\end{align}
Applying this identity to the Cauchy integral theorem for $v''(x)$, we
have
\begin{align}
  0 &= \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y)}{(y-x)^3}\,dy - v''(x) \\
%    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2v^{-}(y)}{(y-x)^3}\,dy - 
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{(y-x)^2 v''(x)}{(y-x)^3}\,dy -
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2v(x)}{(y-x)^3}\, dy -
%    \frac{1}{2\pi i} \int_{\bd\Omega} 
%      \frac{2(y-x)v'(x)}{(y-x)^3}\, dy \\
    &= \frac{1}{2\pi i} \int_{\bd\Omega} 
      \frac{2v^{-}(y) - v''(x)(y-x)^2 - 2v(x) - 2(y-x)v'(x)}
      {(y-x)^3}\, dy.
\end{align}
Since we have constructed the integrand so that it is bounded for for
all $x \in \Omega$, the quadrature error of the trapezoid rule is
acceptable.  Applying the quadrature rule and solving for $v''(x)$, the
Barycentric quadrature rule for the second derivative is
\begin{align}
  v''(x) &\approx \frac{2\sum\limits_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}.
\end{align}
To compute $v(x)$ and $v'(x)$, the Barycentric quadrature rule in
equation~\eqref{eqn:vvpQuadrature} is used. If $x \in \Omega^c$, the
identity
\begin{align}
\frac{1}{x-a} &= -\frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{(y-a)^{-1}}{y-x} dy, 
\end{align}
is used, and the resulting Barycentric quadrature formula is
\begin{align}
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v^{+}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}}
    {\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}.
\end{align}

@@

At each GMRES iteration, we must compute the velocity at each
discretization point on $\bd\Omega$.  To reduce the cost of computing
the velocity, we start by using the trapezoid rule~\eqref{eqn:trap}
accelerated with the fast multipole method (FMM)~\cite{gre-rok1987},
which requires $\mathcal{O}(N)$ operations, and we call this velocity
$v_\trap(\xx)$.  For target points that are sufficiently far from
$\bd\Omega$, $v_\trap(\xx)$ is sufficiently accurate.  However, this
velocity is inaccurate at points that are too close to $\bd\Omega$, and
the velocity must be corrected.  Assuming that $\xx$ is too close to
$\gamma_k$, only the velocity due to $\gamma_k$ must be corrected. We
first subtract the velocity contribution of $\vv(\xx)$ due to
$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
the velocity due to $\gamma_i$ with more accuracy.  That is, the
final velocity is
\begin{align}
  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
    D(\xx,\yy^k_j) \eeta(\yy_j) + v^k_\bary(\xx),
\end{align}
where $v^k_\bary(\xx)$ is the velocity at $\xx$ resulting from applying
the Barycentric quadrature rule due to $\gamma_k$.  This method
naturally extends to points that are close to $\Gamma$, and to the
scenario when $\xx$ is simultaneously close to multiple components of
$\bd\Omega$.

We do not use any fast summation methods to apply the Barycentric
quadrature rule.  Therefore, to it is imperative that we only apply
the Barycentric quadrature at target points where they are required.

The same strategy of using the trapezoid rule and then correcting with
the Barycentric quadrature is used to compute the shear stress on
$\bd\Omega$ and vorticity in $\Omega$.  The trapezoid rule is applied
with a direct summation, but this cost is only incurred once per time
step, and the majority of the computational effort is still required to
compute the velocity using the fast summation method.\todo[inline]{BQ:
Discuss how we don't do Barycentric everywhere since it involves several
$N$ body calculations, while the trapezoid rule only requires a single
one}

@@

}
\end{itemize}
{\color{red}  (Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency)
